Ricci

### 2015-01-26 prep_figures/distribution/scatter-ggvis.Rmd
Better static plots.

source("process.R")
d <- get_results("../../results-rspr/ricci4.mat")
d <- sample(d)  # Shuffle rows of d.

d %>%
  ggvis(x = ~kappa, y = ~dist_jitter) %>%
#  layer_points(size = 5, fill = ~t1_nwk, stroke = ~t2_idx, strokeOpacity := 0) %>%
  layer_points(size = 12, fill = ~t1_nwk) %>%
#  layer_points(size = ~mult, fill = ~t1_nwk, stroke = ~t2_idx) %>%
  # A dummy layer so that we can use text in the tooltip.
  # layer_text(text := ~info, fontSize := 0) %>%
  add_axis("x", grid = FALSE) %>%
  add_axis("y", grid = FALSE, values = 1:3) %>%
  add_legend(c("fill"), properties=legend_props(legend=list(y=0))) 
  #add_legend(c("stroke"), properties=legend_props(legend=list(y=100))) %>%
  #add_legend(c("size"), properties=legend_props(legend=list(y=200))) %>%
  #add_tooltip(function(df) df$info)
```

>>>>

source("process.R")

props <- axis_props(labels=list(fontSize=16), title=list(fontSize=24))

n_taxa <- 7
# walk <- "lazy_unif"
walk <- "unif_prior_mh"

d <- get_results(paste0("../../results-rspr/", walk, "/ricci", n_taxa,".mat"))

d %>%
  ggvis(x = ~kappa, y = ~dist_jitter) %>%
#  layer_points(size = 5, fill = ~t1_nwk, stroke = ~t2_idx, strokeOpacity := 0) %>%
  layer_points(size = 12, fill = ~avg_colless) %>%
#  layer_points(size = ~mult, fill = ~t1_nwk, stroke = ~t2_idx) %>%
  # A dummy layer so that we can use text in the tooltip.
  layer_text(text := ~info, fontSize := 0) %>%
  add_axis("x", title = "κ", grid = FALSE, properties=props) %>%
  add_axis("y", title = "distance", grid = FALSE, values=1:4, properties=props) %>%
#  add_legend(c("fill"), properties=legend_props(legend=list(y=0))) %>%
  #add_legend(c("stroke"), properties=legend_props(legend=list(y=100))) %>%
  #add_legend(c("size"), properties=legend_props(legend=list(y=200))) %>%
#  add_tooltip(function(df) df$info)
  function (x) x # null
```
